Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories

### 2020-09-03 paper/main.tex
tweaked precision/distinctiveness details and fixed panel refs

Examining individual recalls of the same episode event can provide insights into how the above precision and distinctiveness scores may be used to characterize similarities and differences in how different people describe the same shared experience.  In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event (event 22) from different participants: one with a high precision score (P17), and the other with a low precision score (P6).  From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example episode event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.  We used an analogous approach to identify the set of sentences comprising the corresponding recall events for each of the two example participants.  Figure~\ref{fig:precision-detail}C shows excerpts of two participants' recall transcripts that comprised sentences between the first and last descriptions of content from the example episode event.  We then colored all words describing actions and features in the transcripts shown in Panel C according to the color-coded annotations in Panel B.  Visual comparison of these example recalls reveals that the more precise recall captures more of the episode event's content, and in greater detail.

Figure \ref{fig:precision-detail} also illustrates the differences between high and low distinctiveness scores for the same event detailed in Figure~\ref{fig:precision-detail}B (i.e., event 22).  Here, we have extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) matched to the example episode event (Fig.~\ref{fig:precision-detail}F).  We also extracted the annotations for the example episode event, as well as those from each other episode event whose content the example participants' single recall events described (Fig.~\ref{fig:precision-detail}E).  We assigned each episode event a unique color (Panel E) and colored each recalled phrase or sentence (Panel F) according to the episode events they best matched.  Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.

>>>>

Examining individual recalls of the same episode event can provide insights into how the above precision and distinctiveness scores may be used to characterize similarities and differences in how different people describe the same shared experience.  In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event from the participants with the highest (P17) and lowest (P6) precision scores.  From the HMM-identified episode event boundaries, we recovered the set of annotations describing the content of a single episode event (event 22; Fig.~\ref{fig:precision-detail}C), and divided them into different color-coded sections for each action or feature described.  Next, we used an analogous approach to identify the set of sentences comprising the corresponding recall event from each of the two example participants (Fig.~\ref{fig:precision-detail}D).  We then colored all words describing actions and features in the transcripts shown in Panel D according to the color-coded annotations in Panel C.  Visual comparison of these example recalls reveals that the more precise recall captures more of the episode event's content, and in greater detail.

Figure \ref{fig:precision-detail} also similarly illustrates the differences between high and low distinctiveness scores.  We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 22).  We also extracted the annotations for all episode events whose content these participants' single recall events described .  We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recall sentence (Panel F) according to the episode events they best matched.  Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.
